### 2016-03-10 manuscript.Rnw
list versions of packages used to build figure 3

The package vignettes provide two demonstrations of the integration of a
phylogeny and data associated with the taxa it represents. Specifically, the ``Data
mashups'' vignette provides an example of how data associated with tip-taxa can
be gathered and visualized. Another vignette titled ``meta-analysis''
demonstrates how a complete analysis, including the gathering of data and a
phylogeny, can be performed in a single R session. We further demonstrate the
integration of phylogenetic data retrieved using \texttt{rotl} with other data
here. We show how we can obtain a map of the occurrences for some of the cat
species (genus \textit{Lynx}) included in the phylogeny above using records for
these species found in GBIF (Figure~\ref{fig:cat_map}; code available in the
Appendix).

<<cat_map, purl=TRUE, echo=FALSE, size='small', fig.height=4.2, results='hide', message=FALSE, cache=TRUE, fig.cap='GBIF records for the species in \\textit{Lynx} included in the phylogeny associated with the study by \\citealt{Johnson2006}.'>>=
## load required packages
library(rotl)
library(rgbif)
library(ggplot2)
library(maps)

>>>>

The package vignettes provide two demonstrations of the integration of a
phylogeny and data associated with the taxa it represents. Specifically, the ``Data
mashups'' vignette provides an example of how data associated with tip-taxa can
be gathered and visualized. Another vignette titled ``meta-analysis''
demonstrates how a complete analysis, including the gathering of data and a
phylogeny, can be performed in a single R session. We further demonstrate the
integration of phylogenetic data retrieved using \texttt{rotl} with other data
here.

<<cat_map, purl=TRUE, echo=FALSE, size='small', fig.height=4.2, results='hide', message=FALSE, cache=TRUE, fig.cap='GBIF records for the species in \\textit{Lynx} included in the phylogeny associated with the study by \\citealt{Johnson2006}.'>>=
## load required packages. Versions used for the manuscript listed below.
library(rotl)     # v0.5.0
library(rgbif)    # v0.9.2
library(ggplot2)  # v2.1.0
library(maps)     # v3.1.0
